Cover Letter: Replies to Referee

### 2024-02-24 Independence_CH/cover_letter.tex
Fragments of diff
Co-authored-by: Miguel Pagano <miguel.pagano@gmail.com>

\newcounter{LamReplCount}
\setcounter{LamReplCount}{0}
\begin{document}
%
\title{Cover Letter: Replies to Referee
}
%
\titlerunning{Formalization of ctm forcing}%Lessons after formalizing ctm forcing}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Emmanuel Gunther\inst{1} \and
Miguel Pagano\inst{1} \and \\
Pedro Sánchez Terraf\inst{1,2}%\orcidID{0000-0003-3928-6942}
\and
Matías Steinberg\inst{1}
}
%
\authorrunning{E.~Gunther, M.~Pagano, P.~Sánchez Terraf, M.~Steinberg}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universidad Nacional de C\'ordoba. 
  \\  Facultad de Matem\'atica, Astronom\'{\i}a,  F\'{\i}sica y
  Computaci\'on.
  \and
    Centro de Investigaci\'on y Estudios de Matem\'atica (CIEM-FaMAF),
    Conicet. C\'ordoba. Argentina. \\
    \email{\{gunther,sterraf\}@famaf.unc.edu.ar\\
        \{miguel.pagano,matias.steinberg\}@unc.edu.ar}
}
%
\maketitle              % typeset the header of the contribution
%
First and foremost, we are very grateful
for your comments and pointers. After the comments in this cover
letter, you may find useful a version of the paper with highlighted
changes.

>>>>

\newcounter{LamReplCount}
\setcounter{LamReplCount}{0}
\begin{document}
%
\title{Cover Letter: Replies to Referee
}
%
\titlerunning{Formalization of ctm forcing}%Lessons after formalizing ctm forcing}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Emmanuel Gunther\inst{1} \and
Miguel Pagano\inst{1} \and \\
Pedro Sánchez Terraf\inst{1,2}%\orcidID{0000-0003-3928-6942}
\and
Matías Steinberg\inst{1}
}
%
\authorrunning{E.~Gunther, M.~Pagano, P.~Sánchez Terraf, M.~Steinberg}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universidad Nacional de C\'ordoba. 
  \\  Facultad de Matem\'atica, Astronom\'{\i}a,  F\'{\i}sica y
  Computaci\'on.
  \and
    Centro de Investigaci\'on y Estudios de Matem\'atica (CIEM-FaMAF),
    Conicet. C\'ordoba. Argentina. \\
    \email{\{gunther,sterraf\}@famaf.unc.edu.ar\\
        \{miguel.pagano,matias.steinberg\}@unc.edu.ar}
}
%
\maketitle              % typeset the header of the contribution
%
First and foremost, we are very grateful for your comments and
pointers. After the replies in this cover letter, we show the
fragments of the paper with changes; additions and deletions are
highlighted in context. We hope they are useful for you.

Please give us notice if any of the corrections is insufficient.
